---
title: "GY7702 Assignment"
author: "Student ID: 1234567890"
date: "18/12/2020"
urlcolor: blue
output:
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```


# Introduction 

This document was created to meet the requirements of GY7702 R for Data Science at University of Leicester. It was designed and created in R Markdown, a markup language that allows users to create documents that can be formatted to embed code blocks, code outputs and hyperlinks.When the R Markdown file is compiled, the markup language is hidden and the document is displayed in plain text.

This content was created using [R](https://www.r-project.org/), [Rstudio](https://rstudio.com/), [RMarkdown](https://rmarkdown.rstudio.com/) and [GitHub](https://github.com/). 

For further information regarding the source code, data and libraries used in this assignment, please see the project's GitHub page at [https://bit.ly/3arpcv8](https://bit.ly/3arpcv8) (created using [Bitly.com](https://bitly.com/)). 

## Materials 

The libraries used in this assignment: 
```{r load_libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(palmerpenguins)
library(dplyr)
library(knitr)
library(kableExtra)
library(readr)
library(tinytex)
library(lubridate)
library(gridExtra)
library(ggplot2)
```

Contains public sector information licensed under the [Open Government Licence v3.0](http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/): covid19_cases_20200301_20201017.csv and lad19_population.csv. See also [Coronavirus (COVID-19) in the UK](https://coronavirus.data.gov.uk/details/cases) and [Office for National Statistics](https://geoportal.statistics.gov.uk/).

## References

The sudent would like to acknowledge that this document includes teaching materials from Dr Stefano De Sabbata for the module [GY7702 R for Data Science](https://le.ac.uk/modules/2020/gy7702). Stefano's teaching materials can be found [here](https://sdesabbata.github.io/granolarr/)  

R for Data Science by Garrett Grolemund and Hadley Wickham, O’Reilly Media, 2016. [See online book](https://r4ds.had.co.nz/)  


### Note to reader

Where a function is mentioned for the **first time**, a brief explanation will be given before the code block. 
Thereafter, this explanation will be dismissed. 



# Question 1

A vector of 25 numbers between 1 and 7 are listed below. These values represent
answers to a survey question 

```{r}
## NA 3 4 4 5 2 4 NA 6 3 5 4 0 5 7 5 NA 5 2 4 NA 3 3 5 NA
```

*  1 = Completely disagree
*  2 = Disagree
*  3 = Somehow disagree
*  4 = Neither agree or disagree
*  5 = Somehow agree
*  6 = Agree
*  7 = Completely agree
* NA = missing value


## Question 1.1 

Write the code necessary to check whether all participants to the survey either 
completely disagree or completely agree, once the missing values are excluded

 
```{r}
#code
```


```{r}
#code
```

## Question 1.2

**Write the code necessary to extract the indexes related to the participants 
in the survey who at least somehow agree or more.**

```{r}
#code
```


# Question 2

...

# Question 3

... 

# Question 4 

```{r, echo=FALSE}
rm(list = ls())
```
